\documentclass{article}
% \usepackage{showframe}
\usepackage[utf8]{inputenc}
\usepackage[letterpaper, margin=0.75in]{geometry} % US letter is 8.5" by 11"
\usepackage{anyfontsize}
\usepackage{fontawesome}
\usepackage{xparse}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{xfrac}
\usepackage{bm}
\usepackage[super]{nth}
\usepackage{tikz}
\usepackage{amsmath}
\usetikzlibrary{calc, shadings}
\hypersetup{ 
	colorlinks=false, 
	urlbordercolor=blue, 
	pdfborderstyle={/S/U/W 1} % border style will be underline of width 1pt
}
\urlstyle{monospace}
\pagenumbering{gobble}


\graphicspath{{images/}}

\renewcommand{\familydefault}{\sfdefault} % Sans-serif

% \experience: Add a heading for an entry, such as for work experience.
% #1: Title, in large bold
% #2 (optional): Subtitle, directly after a dash after title, in large
% #3 (optional): Subsubtitle, below title, in italics
\makeatletter
\NewDocumentCommand\experience{m O{} O{}}{
	\noindent
	\def\@tempa{#2}
	\begin{large}
		\textbf{#1}\ifx\@tempa\@empty\relax \else\ --- #2\fi \par
	\end{large}
	\def\@tempa{#3}
	\ifx\@tempa\@empty\relax \else \textit{#3} \fi \par
}
\makeatother


% \fancySection: Big section header with a gradient underline
% #1: Section name
\NewDocumentCommand\fancySection{m}{
	\noindent
	\begin{tikzpicture}
		\shade[ left color=black, right color=white, rounded corners=0.5pt]
			($(current page.north)+(-3.5in,-1.6in)$)node[ above right,
			align=left, black ] {\begin{Large}\textbf{#1}\end{Large}} rectangle
			++(3.5in,1pt) ;
	\end{tikzpicture}
}

\begin{document}

\small

\noindent
% Tikz header. 
\begin{tikzpicture}

	% Underline
	\shade[
		left color=black,
		right color=lightgray,
		rounded corners=0.5pt]
	($(current page.north)+(-3.5in,-1.6in)$) rectangle ++(7in,1pt);

	\draw[ultra thick,gray]
	% Vertical line
	($(current page.north)+(0,-0.75in)$) -- ++(0,-0.75in)
	% Name
	node[ midway, left=0cm, text width=3.375in, align=right, black ]
		{\fontsize{32}{38} \selectfont \bf \hspace*{\fill} Daniel
			\hspace*{\fill} Kinsey \hspace*{\fill}}
	% Contact and etc
	node[ midway, right=0.125in, text width=3.25in, minimum height=0.875in,
			align=left, black] {

			{\LARGE \selectfont Software Developer} \hspace*{\fill} \faMapMarker
			\ Ottawa, ON \hspace*{\fill}

			\newpage
			\null % newpage and null to make vfill work
			\vfill

			\faGlobe \ \href{https://kinseyda.com/}{kinseyda.com}
			\hspace*{\fill} \faGithub \
			\href{https://www.github.com/kinseyda}{kinseyda}

			\faLinkedinSquare \
			\href{https://www.linkedin.com/in/daniel-kinsey}{daniel-kinsey}
			\hspace*{\fill} \
			\faEnvelope \
			\href{mailto:daniel.kinsey.dk@gmail.com}{daniel.kinsey.dk@gmail.com}
		};
\end{tikzpicture}

{\centering \parbox[t]{0.75\textwidth}{ {\centering \textbf{Software developer}
and \textbf{summa cum laude computer science graduate} in Ottawa with several
years of experience and a passion for learning new things, programming, and
computers in general.
			\par
		}
}
\par
}

\vspace*{\fill}

\fancySection{Education}

\experience{University of Ottawa}[Honours Bachelor of Science in
	\textbf{Computer Science}][Graduated September 2025]

\begin{itemize}
	\item Graduated with \textbf{highest distinction} / \textbf{summa cum laude}
	\item Graduating CGPA of \textbf{4}\(\sfrac{}{4}\) (OUAC), or
	      \textbf{9.1}\(\sfrac{}{10}\).
	\item \textbf{Dean's Honour List} \(\times\)5, \textbf{Merit Scholarship}
	      recipient \(\times\)2.
\end{itemize}

\vspace*{\fill}

\fancySection{Experience}

\experience{Software Developer (CO-OP)}[Corning Technology Center of Montreal /
	iBwave Solutions][September 2023 --- December 2023]

\begin{itemize}
	\item Developed numerous features for a 2D visualization system for
	      configuring fibre optic cable purchasing, using \textbf{PixiJS} and
	      \textbf{React} with an \textbf{Azure .NET} back-end and
	      \textbf{PostgreSQL}.
	\item Improved a large application in multiple disparate areas, including
	      working with the 2D rendering engine, adding accessibility features
	      such as new ways to display contextual help, and adding more detailed
	      customization to the cabling configurator.
	\item Collaborated in a mid-sized team using agile development practices ---
	      including creating new tickets, performing code reviews, and exceeding
	      performance expectations over several sprints.
\end{itemize}

\experience{Web Developer (CO-OP)}[SkyWare Labs][January 2023 --- April 2023]

\begin{itemize}
	\item Developed web forms and new functionalities for a large scale
	      \textbf{web application} and \textbf{REST} API using
	      \textbf{Angular} (\textbf{Typescript} / \textbf{Javascript}),
	      \textbf{Spring} (\textbf{Java}), and \textbf{PostgreSQL}.
	\item Implemented back-end processing and parsing for ATS message protocols
	      (airport telecommunications), allowing for a large amount of automated
	      data input.
	\item Improved flight path and flight information region visualizations on a
	      map integrated with the Google Maps API via Leaflet, allowing for
	      easier administration of airport data.
\end{itemize}

\vspace*{\fill}

\fancySection{Personal Projects}

I've worked on several open source projects on my \faGithub\
\href{https://github.com/kinseyda}{GitHub}, with write-ups available on my
website, \faGlobe\ \href{https://kinseyda.com/projects}{kinseyda.com/projects}.
Examples include:

\experience{Muziko}[][\faGithub\
	\href{https://github.com/kinseyda/muziko}{muziko},\
	\faGlobe\
	\href{https://kinseyda.github.io/muziko/}{kinseyda.github.io/muziko}]

\begin{itemize}
	\item A \textbf{React} web application for commenting on and sharing music,
	      with a focus on \textbf{accessibility} and \textbf{user experience}.
	\item Features include searching via the Spotify API, authentication via
	      Firebase, with comments and user data stored in Firestore.
\end{itemize}

\experience{Neural Playground}[][\faGithub\
	\href{https://github.com/kinseyda/neural-playground}{neural-playground},\
	\faGlobe\
	\href{https://kinseyda.github.io/neural-playground/}{kinseyda.github.io/neural-playground}]

\begin{itemize}
	\item A \textbf{Vue.js} web application for visualizing and experimenting
	      with neural networks, utilizing a from-scratch implementation of a
	      neural network and the backpropagation algorithm in
	      \textbf{Typescript}.
	\item Features include visualizing the network structure using
	      \textbf{vis.js}, allowing for real-time visualization of the network
	      training process.
\end{itemize}

\vspace*{\fill}

\fancySection{Skills}

\begin{itemize}
	\item \textbf{Languages:} C, C\#, Python, Java, Typescript/Javascript,
	      HTML/CSS, SQL, Bash.
	\item \textbf{Frameworks:} React, Angular, PixiJS, Node.js, Express.js,
	      Spring Boot.
	\item \textbf{Tools:} Git, Docker, PostgreSQL, Firebase/Firestore,
	      Microsoft Azure.
	\item \textbf{Other:} Agile development practices, REST APIs, SQL and NoSQL
	      databases, server administration.
	\item \textbf{Interests:} Machine learning, web development, game
	      development, music composition and theory.
\end{itemize}


\end{document}